An Improved ANS Transaction Template

### 2018-01-27 paper.tex
updated conclusion

The JCPOA aggrement limits to 5060 runing centrifuges in the Natanz Fuel
Enrichment Plant (NFEP) so about $10\%$ of its design capacity, the reference
case allows to build $1$ SQ of HEU in 8 months (versus in 24 days without the JCPOA
agrement limitations). While using directly the 5060 centrifuges to produce 1 SQ
of HEU take about 8 months, case 1 and the case 2 will produce it in 2 years.
Nevertheless the diversion scenario from case 1 or 2 will be hard if not
impossible to detect from the cascasde configuration.

While the results of this work might be limited, it aims to develop a
methodology to study diversion scenarios, from the fuel cycle perspective.
Futhermore, additional methods to compute the CascadeEnrich response to
non-ideal feed assay will be investigated.  The CascadeEnrich facility used will
also be improved in order to take advantage of the dynamical flow managment of
the Cyclus framework, allowing for example to automatically assign the cascade
to the different level as the need evolve.

>>>>

The JCPOA agreement limits the Natanz Fuel Enrichment Plant (NFEP) to 5060 operating centrifuges, or about $10\%$ of its design capacity. The reference case, using all 5060 centrifuges in a single cascade, would lead to a stockpile of approximately $1$ SQ of HEU in 8 months, as opposed to 24 days without the
JCPOA agreement limitations. However, the more realistic case 1 and the case 2 will produce a $1$ SQ in about 2 years. Nevertheless, the diversion scenario from case 1 or 2 would be much more difficult to detect from the cascade configuration.

While the results of this work might be limited, it aims to develop a
methodology to study diversion scenarios from the fuel cycle perspective. Furthermore, additional methods to compute the CascadeEnrich response to non-ideal feed assays will be investigated in the future.  The CascadeEnrich facility will be improved in order to take advantage of the dynamic flow management of the Cyclus framework. This will include automatic cascade level assignment to optimize the analysis workflow.
